---
title: "DPSS Capstone"
author: "Alex Ford"
date: "7/18/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r, include = FALSE}
library(tidyverse)
library(jsonlite)
library(sf)
library(tidycensus)
library(haven)
library(tinytex)
library(knitr)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(stargazer)
```


# The United States Hate Crime Rate


The FBI defines a hate crime as a violent or property crime -- such as a murder, arson, assault, or vandalism -- that is “motivated in whole or in part by an offender’s bias against a race, religion, disability, sexual orientation, ethnicity, gender, or gender identity”) each year (Swathi Shanmugasundaram, "Hate Crimes Explained", 2018).

```{r gathering_data, include = FALSE, results="hide"}
census_api_key("376fa29de766d259d95581e8e6ede8addb6a9b7b") #install=TRUE

vars <- load_variables(2016, "acs5")

census_data <- get_acs(
  geography = "state",
  geometry = TRUE,
  shift_geo = TRUE,
  variables = c(
    total_pop = "B01003_001",
    household_income = "B19001_001",
    unemployed_pop = "B23025_007",
    hs_diploma_pop = "B15003_017",
    white_pop = "B02001_002",
    poverty_pop = "B05010_001",
    acs_gini = "B19083_001"),
  year = 2016,
)

census_data <- census_data %>%
  select(-moe) %>%
  spread(variable, estimate)

census_data <- census_data[-c(9),]

census_data <- census_data %>%
  mutate(
    pct_unemployed = unemployed_pop / total_pop,
    pct_hs_only = hs_diploma_pop / total_pop,
    pct_poor_white = white_pop / poverty_pop,
    pct_non_white = (total_pop - white_pop) / total_pop
  )

regions <- read_csv("ucb_regions.csv") %>%
  select(-"State Code")

census_data <- census_data %>%
  left_join(regions, by = c("NAME" = "State"))

kaiser_non_citizen <- read_csv("kaiser_citizen_data.csv") %>%
  select(-total)

census_data <- census_data %>%
  left_join(kaiser_non_citizen, by = "NAME")

fbi_data <- read_csv("fbi_agency_hc_reporting_by_state_2017.csv") %>%
  mutate(hate_crimes_per_100k = total_reported_incidents / pop_covered * 100000)

census_data <- census_data %>%
  left_join(fbi_data, by = c("NAME" = "Participating_state"))

pupil_spending <- read_csv("pupil_spending.csv")
census_data <- left_join(census_data, pupil_spending, by = c("NAME" = "State"))

body_cam <- read_csv("body_cam_data.csv")
census_data <- left_join(census_data, body_cam, by = c("NAME" = "state"))

```

```{r, echo=FALSE}
ggplot() +
  geom_sf(
    data = census_data,
    aes(fill = hate_crimes_per_100k)) +
  scale_fill_distiller(
    palette = "Blues",
    type = "seq",
    direction = "1",
    guide = "colorbar"
  ) +
  theme_void() +
  labs(
    title = "Hate Incident Rates",
    subtitle = "Hate incidents per 100,000 residents in 2017.",
    caption = "Source: FBI"
  ) +
  theme(
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, size = 8, face = "italic")
  )
```

In order to reduce the number of hate crimes, it’s important to innovate not only our approach to data collection as a baseline upon which to analyze and reform our practices, but also to consider the factors of American that could influence the rate of hate crimes. Racism itself is pervasive and stubborn, and not something easily deconstructed; however it is our responsibility to consider the ways in which we could ameliorate its contributing factors, such as income inequality and real or perceived disenfranchisement.

\pagebreak

**Data Issues**  
As the Bureau of Justice Statistics states, 250K people are victimized by hate crimes in the United States each year; however, FBI data shows a much lower number. In their annual report, the FBI estimates between five- to six-thousand incidents occurring nationwide ("Hate Crime", Bureau of Justice Statistics (BJS)). 


<br>


```{r, include = FALSE, results="hide"}

hate_crimes_us_main <- read_csv("us_hate_crime_data.csv")

hate_crimes_us_main <- hate_crimes_us_main %>%
  mutate(
    us_hate_crimes_per_100k = us_hate_crime / total_us_pop * 100000,
    us_crimes_per_100k = total_us_crimes / total_us_pop * 100000
  )

```


```{r, echo=FALSE}

ggplot(data = hate_crimes_us_main, aes(x = year, y = us_hate_crimes_per_100k)) +
  geom_bar(stat = "identity", position = "dodge", fill ="tomato3", width = .75) +
  scale_x_discrete("Year", limits = c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017), expand = c(0,0)) +
  scale_y_continuous("Hate Crimes per 100K", expand = c(0,0), breaks = c(0, 0.5, 1, 1.5, 2, 2.5, 3), limits = c(0, 3)) +
  ggtitle("US Hate Crime Incident Reports Over Time") +
  labs(caption = "Source: FBI") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle=65, vjust = 0.6),
    axis.title.x = element_text(margin = margin(t = 15, r = 20, b = 1, l = 1)),
    axis.title.y = element_text(margin = margin(t = 5, r = 20, b = 1, l = 1)),
    plot.title = element_text(hjust = 0.5)
  )
```

**Inconsistent Protections**  
While the federal government and 45 states (all but Arkansas, Georgia, Indiana, South Carolina, and Wyoming) have passed hate crime legislation that enhances penalties for the crime itself, laws vary on their definition of what constitutes a hate crime and which groups are protected (Shanmugasundaram, "Hate Crimes"). While all laws cover bias against race, ethnicity, and religion, many lack statutes on gender, disability, sexual orientation, and gender identity. Enforcing these laws brings challenges of their own: only 12 states have laws requiring that officers be trained to identify and investigate hate crimes, according to the Southern Poverty Law Center (Shanmugasundaram, "Hate Crimes").  

**Voluntary Reporting by Agencies**  
Perhaps our biggest obstacle is that reporting to the UCR program is entirely voluntary, which renders the data available incomplete. Some states, such as Hawaii, submit no data at all, leading to a dearth of data and a roughly 15% participation rate.  

In addition, the UCR program collects data on a specific subset of hate crimes that are relevant to the organization, prosecutable hate crimes, which make up only a fraction of total hate crimes. A more accurate data set would include not only prosecutable hate crimes but offenses that are non-prosecutable, such as circulation of discriminatory literature (Shanmugasundaram, "Hate Crimes").  

**Trust Concerns**  
As members of communities that have historically been marginalized and exploited by institutions, victims of hate crimes are also less likely to report their experiences to authorities.  

Around the time of the last presidential election, the public expressed concern about a spike in hate crimes. “In the first 34 days after the election, the SPLC documented 1,094 bias-related incidents and found that 37% of them directly referenced Trump, his campaign slogans or his notorious comments about sexual assault.”  

Former FBI director James Comey, while introducing the 2015 hate crimes report said, “We need to do a better job of tracking and reporting hate crimes to fully understand what is happening in our communities and how to stop it.” In a 2015 report, the Justice Research and Statistics Association (JRSA) petitioned for a broader and deeper approach to collecting data on and strategizing about crime in the United States.  

**Correlations with Hate Crimes**  
Analysis by the FBI and groups like the Southern Poverty Law Center has shown correlation between levels of income inequality and incidences of hate crimes, a correlation that was shown again by Five-Thirty-Eight in the wake of the 2016 general election (Maiamajumder, "Higher Rates Of Hate Crimes Are Tied To Income Inequality", 2017).  

Research dating from 1968 by economist Gary S. Becker states that more violence is likely in areas with wider socioeconomic gaps, as potenital criminals perceive greater returns (Pinsker, "Does Inequality Cause Crime?", 2014). This sort of cost-benefit analysis is a common refrain in discussions of strife, but it's worth drilling down further to see what more nuances can be ascertained.  

The main variables included in this assessment of rate of hate crimes include a series of measures of wealth, education, employment, and diversity: median household income, the percent of the population that is unemployed, the percent of the population with only a high school degree, the percent of whites below the poverty line, the GINI index (a measure of income disparity), the percent of the population that is non-white, and the percent of the population that are not US citizens.  

In addition, I’ve chosen to include a variable that may influence the level of hate crimes: total expenditure per public school student per state; and a variable that may influence the likelihood of an agency to report: whether or not an agency has made at least one effort toward policing transparency (required the use of body cameras on officers, requested funding for the institution of body cameras on officers, or created open record laws). By using these two additional variables, I hope to assess the impact on the rate of hate crimes and rate of reporting, respectively. Interaction terms are used on wealth and wealth-adjacent variables of household income, percent unemployed, and the GINI index.  

```{r, include = FALSE, results="hide", warning = FALSE, message = FALSE}
regression1 <- lm(
  hate_crimes_per_100k ~
    household_income +
    pct_unemployed +
    pct_hs_only +
    pct_poor_white +
    acs_gini +
    pct_non_white +
    pct_non_citizen +
    total_spending_per_pupil +
    at_least_one_effort,
  data = census_data)
summary(regression1)

regression2 <- lm(
  hate_crimes_per_100k ~
    household_income*pct_unemployed*acs_gini +
    pct_hs_only +
    acs_gini +
    pct_poor_white +
    pct_non_white +
    pct_non_citizen +
    total_spending_per_pupil +
    at_least_one_effort,
  data = census_data)
summary(regression2)
```

```{r mylatextable, results = "asis", echo = FALSE, warning=FALSE}
stargazer(regression1, type = 'latex')
stargazer(regression2, type = 'latex')
```


Our regression showed statistical significance with the variables of percent only high school-educated, percent non-citizen, and the total expenditure per public school student.  

```{r, warning = FALSE, echo=FALSE}

ggplot(
    census_data,
    aes(x = NAME, y = hate_crimes_per_100k, colour = factor(at_least_one_effort))
    ) +
  geom_point() +
  theme(
    axis.text.y = element_text(size = 5, hjust = 0.95, vjust = 0.2),
    axis.title.x = element_text (size = 8, hjust = 0.5),
    axis.title.y = element_blank(),
    plot.caption = element_text(size = 5, hjust = 0.5, face = "italic"),
    plot.title = element_text(hjust = 0.5)
  ) +
  coord_flip() +
  labs(
    title = "State Policing Transparency Initiatives",
    caption = "Indicates that states have requirements for or allocated funding for body cameras, and/or have open record laws. Source: NCSL.",
    y = "Hate Crimes per 100K"
  ) +
    scale_color_manual(
      name = "Initiative Taken",
      labels = c("Yes", "No"),
      values = c("royalblue2", "seagreen2"),
      guide = 'legend'
  )


```

**Progressive Policing Policies**  
While our data used to assess the likelihood of a given state’s agencies to embrace more progressive transparency measures, it is limited and binary. Other factors may influence the decision (such as public scandal)  that cannot be untwined from rate of hate crimes. It would be interesting to continue this research using more qualitative and quantitative data -- interviewing and gathering data by agency/district (NCSL, "Civil and Criminal Justice", 2019).  

**Public School Funds Allocation**  
In this intuition, a state that devotes more funds to public school pupil has a more well-supported public school network, likely a more diverse learning environment. Well-funded public schools would also indicate citizen support for and use of the public school system (as opposed to private or charter schools), which could imply a greater popular comfort with diversity.  

While this variable does show some statistical significance, the regression line is interesting. I would like to repeat the test replacing dollar value with percent of state budget for a more accurate picture, and perhaps include more measurements of the educational system (US Census Bureau, "2017 Public Elementary-Secondary Education Finance Data", 2017).  

```{r, include = FALSE, warnings = "FALSE"}
ggplot(census_data, aes(x = total_spending_per_pupil)) +
  theme_bw() +
  geom_smooth(aes(y = hate_crimes_per_100k)) +
  labs(
    x = "State Spending per Student",
    y = "Hate Crimes per 100K",
    colour = "Hate Crimes"
  ) +
  theme(
    plot.title = element_text(hjust = 0.5)
  ) +
  ggtitle("State Spending per Public School Student & Hate Crimes per 100K")
```

\pagebreak

**Conclusion**

As a final assessment of our data, I analyzed the differences in reported incidents between the United States and the United Kingdom. While at first glance it may appear that the United Kingdom is experiencing a vastly higher proportion of hate crimes, what is more likely is that their reporting process is more rigorous and regulated.

```{r, include = FALSE, warnings = "FALSE"}
hate_crimes_us <- hate_crimes_us_main %>%
  select(year, us_hate_crime, total_us_pop, total_us_crimes, us_hate_crimes_per_100k, us_crimes_per_100k) %>%
  filter(year >= 2012)

hate_crimes_uk <- read_csv("uk_hate_crime_data.csv") %>%
  mutate(
    uk_hate_crimes_per_100k = uk_hate_crime / total_uk_pop * 100000,
    uk_crimes_per_100k = total_uk_crimes / total_uk_pop * 100000
    )

hate_crimes_us_vs_uk <- hate_crimes_us %>%
  left_join(hate_crimes_uk, by = "year") %>%
  select(year, us_hate_crimes_per_100k, us_crimes_per_100k, uk_hate_crimes_per_100k, uk_crimes_per_100k)

hate_crimes_us_vs_uk_plot <- hate_crimes_us_vs_uk %>%
  gather(type, crimes_per_100k, -year) %>%
  mutate(place = str_sub(type, 1, 2)) %>%
           mutate(type = str_sub(type, 4, 7))

hate_crimes_us_vs_uk_plot <- with(hate_crimes_us_vs_uk_plot, hate_crimes_us_vs_uk_plot[order(year, type, place),])

```

```{r, echo=FALSE}

ggplot(data = hate_crimes_us_vs_uk_plot, aes(x = place, y = crimes_per_100k, fill = type)) +
  geom_bar(stat = "identity") +
  facet_grid(~year) +
  theme_light() +
  labs(
    title = "UK vs. US Crime Reporting, 2012-2017",
    x = "",
    y = "Crimes per 100K",
    fill = "Breakdown",
    caption = "Source: Statistica"
  ) +
  scale_fill_manual(
    labels = c("Total", "Hate"), values = c("skyblue", "tomato1")) +
  theme(
    plot.title = element_text(size = 12, margin = margin(t=20, b=20), hjust = 0.5),
    axis.text.x = element_text(angle=65, vjust = 0.6),
    axis.text.y = element_text(size = 6, margin = margin(l = 10))
  )

```


This chasm should spur the United States to be more serious in our data collection undertakings -- through actions such as incentivizing and training local authorities-- especially with respect to the unfortunate nature of the crimes occurring, and to advocate more intently to protect our historically vulnerable groups.  

\pagebreak

*Sources*  

"Civil and Criminal Justice." Civil and Criminal State Legislative Issues | Bill Tracking. Accessed July 19, 2019. http://www.ncsl.org/research/civil-and-criminal-justice.aspx.

"Crime in England and Wales 2019." Statista. Accessed July 19, 2019. https://www.statista.com/statistics/283069/recorded-crimes-in-england-and-wales-uk-y-on-y/.

"Hate Crime." Bureau of Justice Statistics (BJS). Accessed July 19, 2019. https://www.bjs.gov/index.cfm?ty=tp&tid=37.

Maiamajumder. "Higher Rates Of Hate Crimes Are Tied To Income Inequality." FiveThirtyEight. January 23, 2017. Accessed July 19, 2019. https://fivethirtyeight.com/features/higher-rates-of-hate-crimes-are-tied-to-income-inequality/.

Pinsker, Joe. "Does Inequality Cause Crime?" The Atlantic. October 23, 2014. Accessed July 19, 2019. https://www.theatlantic.com/business/archive/2014/10/does-inequality-cause-crime/381748/.

Shanmugasundaram, Swathi. "Hate Crimes, Explained." Southern Poverty Law Center. April 15, 2018. Accessed July 19, 2019. https://www.splcenter.org/20180415/hate-crimes-explained.

US Census Bureau. "2017 Public Elementary-Secondary Education Finance Data." 2017 Public Elementary-Secondary Education Finance. April 19, 2019. Accessed July 19, 2019. https://www.census.gov/data/tables/2017/econ/school-finances/secondary-education-finance.html.









